---
title: "Aggregates in R"
subtitle: "A/B Testing"
output: html_notebook
---


### Loading libraries and data  

```{r message = FALSE, error=TRUE}
# loading packages
library(readr)
library(dplyr)
library(ggplot2)
```

```{r message = FALSE, error=TRUE}
# loading "ad_clicks" data
ad_clicks <- read_csv("ad_clicks.csv")
```

### Analyzing data  

1.
Inspect the first few rows of ad_clicks using head().

```{r error=TRUE}
# inspect ad_clicks here:
head(ad_clicks)
```

`ad_clicks` contains the following columns:

- user_id: unique user id
- utm_source: where user saw the ad. UTM stands for Urchin Tracking Module
- day: the day the ad was seen
- ad_click_timestamp: the time the ad was clicked
- ad_clicked: boolean indicating if ad was clicked (TRUE or FALSE)
- experimental_group: which ad version was shown (A or B)

2.
Your manager wants to know which ad platform is getting the most views.

How many views (i.e., rows of the data frame) came from each utm_source? 

```{r error=TRUE}
# define views_by_utm here:
views_by_utm <- ad_clicks %>% 
  group_by(utm_source) %>%
  summarize(count = n()) %>%
  arrange(-count)
views_by_utm
```
`views_by_utm` has the following counts:

email: 255 views
facebook: 504 views
google: 680 views
twitter: 215 views

3.
We want to know the percentage of people who clicked on ads from each utm_source. Let’s start by finding the number of clicks per utm_source.

```{r error=TRUE}
# define clicks_by_utm here:
clicks_by_utm <- ad_clicks %>% 
  group_by(utm_source, ad_clicked) %>%
  summarize(count = n()) %>%
  arrange(utm_source)
clicks_by_utm

table(ad_clicks$ad_clicked)
```
`clicks_by_utm` showed the following counts for each utm_source/ad_clicked grouping:

- email/FALSE (not clicked): 175
- email/TRUE (clicked): 80
- facebook/FALSE (not clicked): 324
- facebook/TRUE (clicked): 180
- google/FALSE (not clicked): 441
- google/TRUE (clicked): 239
- twitter/FALSE (not clicked): 149
- twitter/TRUE (clicked): 66


4.
To find the percentage of people who clicked on ads from each utm_source, we need to add a new column to ad_clicks that stores the count of clicks (or the count of not clicking) divided by the total number of ad views.  

5.
Filter percentage_by_utm to remove all rows that do not describe clicked ads, and view it.

```{r error=TRUE}
# define percentage_by_utm here:
percentage_by_utm <- clicks_by_utm %>%
  group_by(utm_source) %>%
  mutate(percentage = count/sum(count)) 
percentage_by_utm

percentage_by_utm$percentage <- round(percentage_by_utm$percentage, 
  digits=3)
percentage_by_utm

# filtering percentage
true_clicks <- percentage_by_utm %>%
  filter(ad_clicked == TRUE) %>%
  arrange(-percentage)
true_clicks
```

- `count` represents the number of users who did or did not click on an ad
- `sum(count)` represents the total number of users who saw the ad  

`percentage_by_utm` will now contain the click and non-click rates for each utm_source/ad_clicked grouping.  

In order of most effective `utm_source`:

- facebook: 35.7% of viewers clicked the ad
- google: 35.1% of viewers clicked the ad
- email: 31.4% of viewers clicked the ad
- twitter: 30.7% of viewers clicked the ad


### Performing A/B Test

6.
The column experimental_group tells us whether the user was shown ad A or ad B.

Were approximately the same number of people shown both ads? Group _ad_click_ by _experimental_group_ and count the rows, saving your result to _experiment_split_.

```{r error=TRUE}
# define experiment_split here:
experiment_split <- ad_clicks %>%
  group_by(experimental_group) %>%
  summarize(count = n())
experiment_split
```

We can see that there was an equal number of users (827) in each experiment group.



7.
Using group_by() and the columns ad_clicked and experimental_group, check to see if a greater number of users clicked on ad A or ad B. Save your result to `clicks_by_experiment`, and view it.

```{r error=TRUE}
# define clicks_by_experiment here:
clicks_by_experiment <- ad_clicks %>%
  group_by(experimental_group, ad_clicked) %>%
  summarize(count = n()) %>% 
  mutate(percentage = count/sum(count))

clicks_by_experiment$percentage <- 
  round(clicks_by_experiment$percentage, digits=3)
clicks_by_experiment

true_experiment_clicks <- ad_clicks %>%
  group_by(experimental_group) %>%
  filter(ad_clicked == TRUE) %>% 
  summarize(count = n()) %>% 
  mutate("TrueClicks%" = count/sum(count))
true_experiment_clicks
```
A greater number of users clicked Ad A (310) than Ad B (255).



8.
The Product Manager for the A/B test thinks that the clicks might have changed by day of the week.

Create two data frames: a_clicks and b_clicks, which contain only the results for A group and B group, respectively.
```{r error=TRUE}
# define a_clicks here:
a_clicks <- ad_clicks %>% 
  filter(experimental_group == "A")

# define b_clicks here:
b_clicks <- ad_clicks %>%
  filter(experimental_group == "B")
```


9.
For each data frame (*a_clicks* and *b_clicks*), we want to find the number of users who clicked on the ad (and did not click on the ad) by day. Save the results to _a_clicks_by_day_ and _b_clicks_by_day_, and view them.
```{r error=TRUE}
# define a_clicks_by_day here:
a_clicks_by_day <- a_clicks %>%
  group_by(day,ad_clicked) %>%
  summarize(count=n())
a_clicks_by_day

# define b_clicks_by_day here:
b_clicks_by_day <- b_clicks %>%
  group_by(day,ad_clicked) %>%
  summarize(count=n())
b_clicks_by_day
```

10.
To find the percentage of people who clicked on the ads from each _day_, we need to add a new column to _a_clicks_by_day_ and _b_clicks_by_day_ that stores the _count_ of clicks (or the _count_ of not clicking) divided by the total number of ad views.  

11.
Filter _a_percentage_by_day_ and _b_percentage_by_day_ to remove all rows that do not describe clicked ads, and view them.  

```{r error=TRUE}
# define a_percentage_by_day here:
a_percentage_by_day <- a_clicks_by_day %>%
  group_by(day) %>%
  mutate(percentage = count/sum(count)) %>% 
  filter(ad_clicked==TRUE) %>% 
  mutate(group = "A")
a_percentage_by_day

# define b_percentage_by_day here:
b_percentage_by_day <- b_clicks_by_day %>% 
  group_by(day) %>%
  mutate(percentage = count/sum(count)) %>%
  filter(ad_clicked==TRUE) %>%
  mutate(group = "B") 
b_percentage_by_day
```


12. Joining data frames to plot
```{r}
# joining a & b dfs 
dfs <- full_join(a_percentage_by_day,b_percentage_by_day) 
dfs
```


13. Plotting 
```{r}
# plot with facet wrap by group 
comparison1 <- ggplot(dfs, aes(day, percentage)) + 
  geom_bar(stat='identity') +
  labs(title = "Percentage of Clicks by Days", 
  x= "Days", y='Percentage') + 
  theme(axis.text.x = element_text(angle = 90)) +
  facet_wrap(~group) 

comparison1
```

We can see that there's a difference in click rates for each day.   
Ad `A` outperformed ad `B` on every day of the week except Tuesday and Sunday, so **A** is the better choice.


 